\documentclass{muratcan_cv}

\setname{Brandon Cano}{}
\setaddress{Iowa City, Iowa}
\setmobile{319-531-0040}
\setmail{brandoncano01@gmail.com}
\setlinkedinaccount{https://www.linkedin.com/in/brandon-cano/}
\setgithubaccount{https://github.com/bmcano}
\setgoogleplayaccount{https://play.google.com/store/apps/dev?id=6118139973869195471}
\setthemecolor{MidnightBlue}
\usepackage{fontspec}
\usepackage{fontawesome}
\usepackage{geometry}
\geometry{margin=1.5cm}

\begin{document}

\headerview
\vspace{2ex}

\section{Skills}
	\newcommand{\skillone}{\createskill{Programming Languages}{Kotlin \cpshalf Java \cpshalf JavaScript \cpshalf TypeScript \cpshalf HTML/CSS \cpshalf Python}}
	
	\newcommand{\skilltwo}{\createskill{Frameworks \& Libraries}{Jetpack Compose \cpshalf Android SDK \cpshalf MVVM \cpshalf XML Layouts \cpshalf Material 3}}

	\newcommand{\skillthree}{\createskill{Technologies}{Git \cpshalf GitLab/GitHub \cpshalf Firebase \cpshalf SQL/Room \cpshalf REST APIs \cpshalf LaTeX}}

	\createskills{\skillone, \skilltwo, \skillthree}
\section{Work Experience}
	\datedexperience{Software Engineer}{August 2024 - Present} 
	\explanation{State Farm}{Bloomington, IL} 
	\explanationdetail{ 
		\smallskip 
		\coloredbullet\ %
		Developing and maintaining features for the State Farm Mobile App as an Android developer.
		
		\smallskip 
		\coloredbullet\ %
		Implemented RESTful web services with JSON data handling in MVVM-based screens to modernize the app.
		
		\smallskip 
		\coloredbullet\ %
		Designed blueprints for common screen patterns to ensure UI/UX consistency across the app.
		
		\smallskip
		\coloredbullet\ %
		Utilize Firebase Crashlytics for real-time crash reporting and monitoring app stability.
		
		\smallskip
		\coloredbullet\ %
		Leveraged Firebase Remote Config to manage feature flags and to dynamically adjust app behavior.
		
		\smallskip
		\coloredbullet\ %
		Continuous collaboration with various teams to review specifications for new features and changes.
		
		\smallskip
	}
	\datedexperience{Software Engineer - Intern}{May 2022 - August 2024} 
	\explanation{State Farm}{Bloomington, IL} 
	\explanationdetail{ 
		\smallskip 
		\coloredbullet\ %
		Contributed Kotlin-based feature enhancements to the State Farm Mobile App.

		\smallskip
		\coloredbullet\ %
		 Migrated legacy Java screens to Kotlin and Jetpack Compose, improving maintainability.
		 
		\smallskip
		\coloredbullet\ %
		Implemented MVVM screen modules to separate UI from logic, improving testability and reuse.
		
		\smallskip
		\coloredbullet\ %
		Wrote JUnit unit tests for core utility modules, raising coverage and catching edge-case bugs.
		
		\smallskip
		\coloredbullet\ %
		Independently assessed feature changes to ensure complete platform functionality.

		\bigskip
	} 
\section{Education} 
	\datedexperience{Master of Science - Electrical and Computer Engineering}{August 2023 - May 2025}
	\explanation{University of Iowa}{Iowa City, IA}
	\explanationdetail{
		\smallskip
		\coloredbullet\ %
		3.5/4.0 GPA

		\coloredbullet\ %
		Specialization in Software Engineering
		
		\coloredbullet\ %
		Participated in undergrad-to-graduate (U2G) 5 year plan

		\smallskip
	}
	\datedexperience{Bachelor of Science in Engineering - Computer Engineering}{August 2020 - May 2024}
	\explanation{University of Iowa}{Iowa City, IA}
	\explanationdetail{

		\smallskip
		\coloredbullet\ %
		3.7/4.0 GPA - Dean's List

		\coloredbullet\ %
		Minor in Mathematics
		
		\bigskip
	}
\section{Notable Projects}
	\datedexperience{Electrical Component Calculator Suite \textmd{| Android Apps}}{June 2022 - Present}
	\explanationdetail{
		\smallskip 
		\coloredbullet\ %
		Independently built Android apps for calculating values of resistors, capacitors, inductors, etc.

		\smallskip
		\coloredbullet\ %
		Utilized Kotlin and Jetpack Compose UI with Android Studio to build the apps.

		\smallskip 
		\coloredbullet\ %
		Created custom-built library to manage shared code, improving maintainability across all apps.
		
		\smallskip
		\coloredbullet\ % 
		Continuously enhancing product functionality and resolved technical challenges to optimize performance.
		
		\smallskip
		\coloredbullet\ %
		Combined 100,000+ downloads across all four apps on the \href{https://play.google.com/store/apps/developer?id=Brandon+Cano}{Google Play store}.

		\smallskip
	}
	%
	\datedexperience{Graduate Admissions Portal \textmd{| Full-Stack Web App}}{January 2025 -- May 2025}
	%\explanation{Software Engineering I (Academic Project)}{University of Iowa}
	\explanationdetail{
  	\smallskip
  	\coloredbullet\ Led a 4-member Scrum team over six 2-week sprints—facilitating planning, stand-ups, reviews, and retrospectives.

  	\smallskip
  	\coloredbullet\ Designed and implemented a NestJS + TypeORM backend (PostgreSQL) and a Next.js frontend with TypeScript. 

  	\smallskip
  	\coloredbullet\ Built weighted scoring engine, reviewer assignment dashboards, and document upload/preview modules in sprint increments. 
  	
  	\smallskip
  	\coloredbullet\
  	Wrote Jest unit tests targeting over 70\% coverage to ensure reliability of core application logic.

  	\smallskip
  	\coloredbullet\ Deployed on AWS EC2 using Nginx as a reverse proxy, to managed the domain, and SSL certificates.

	}
\end{document}
